Data Preparation

### 2019-01-09 Data Preparation.Rmd
Generating variables at the course level

>>>>

## Course Data
Now that we have a clear overview of the distribution of AoDs (`d_AoD`) and assessments (`d_assessment`) among the courses, let us add variables to the tibble `d_course` that contain the information at the course level. The tibble `d_ILO_detail` contains two columns indicating the code of the course and the number of ILOs it contains; `d_assessment_detail` contains three columns indicating the code of the course, the number of assessments it covers and a list of the assessments it covers; `d_AoD_detail` contains three columns indicating the code of the course, the number of AoD it covers and a list of the AoD it covers. We use a `full_join` to add these variables to the tibble `d_course`.
```{r}
d_ILO_detail <- d_ILO %>% 
  select(Code, ILO) %>%
  unique %>%
  count(Code) %>%
  rename(n_ILO = n)
print(d_ILO_detail)

d_assessment_detail <- d_assessment %>%
  group_by(Code) %>%
  summarise(n_assessment = n(),
            `Assessments Covered` = paste(Assessment, collapse = ", "))
print(d_assessment_detail)

d_AoD_detail <- d_AoD %>%
  group_by(Code) %>%
  summarise(n_AoD = n(),
            `AoD Covered` = paste(AoD, collapse = ", "))
print(d_AoD_detail)
```
